---
title: "Annex2_2"
author: "Alejandro Vaca"
date: "3/3/2018"
output: word_document
---

In the first chunk, the whole data mining and transformation process is performed, using the same code as in the previous part of Annex 2. However, as the directory must be changed. This is because in Annex2, as seen in previous code, a generic function to read all csv is used. In this section, we need to read also, but separately, all data from Google Trends. This means that if we do not choose a new directory with all the cryptocurrencies' csvs plus the google trends csvs, our generic function would read the latter also; therefore the data for the beginning of Annex 1 would not work. For this reason, the first thing to do for running this Rmd is to choose as a directory (in my computer): ~Documents/TFG/google_interest_portfolio_selection. For the first part of the Annex 1 (the Rmd previous to this), the directory: ~Documents/TFG/portfolio_analysis_tfg should be chosen. 
```{r}

library(readr)
btc <- read_csv('btc.csv')
dash <- read_csv('dash.csv')
eth <- read_csv('eth.csv')
iota <- read_csv('iot.csv')
lsk <- read_csv('lsk.csv')
maid <- read_csv('maid.csv')
neo <- read_csv('neo.csv')
xem <- read_csv('xem.csv')
xmr <- read_csv('xmr.csv')
xrp <- read_csv('xrp.csv')
zec <- read_csv('zec.csv')

btc = data.frame(btc)
dash = data.frame(dash)
eth = data.frame(eth)
iota = data.frame(iota)
lsk = data.frame(lsk)
maid = data.frame(maid)
neo = data.frame(neo)
xem = data.frame(xem)
xmr = data.frame(xmr)
xrp = data.frame(xrp)
zec = data.frame(zec)


btc = btc[ , 2:5]
dash = dash[ , 2:5]
eth = eth[ , 2:5]
iota = iota[ , 2:5]
lsk = lsk[ , 2:5]
neo = neo[ , 2:5]
xem = xem[ , 2:5]
xmr = xmr[ , 2:5]
xrp = xrp[ , 2:5]
zec = zec[ , 2:5]
maid = maid[ , 2:5]


btc$volatility = btc[,3] - btc[,4]
dash$volatility = dash[,3] - dash[,4]
#we cannot use eos because there is no data about its volatility (high -low)
eth$volatility = eth[,3] - eth[,4]
iota$volatility = iota[,3] - iota[,4]
lsk$volatility = lsk[,3] - lsk[,4]
neo$volatility = neo[,3] - neo[,4]
xem$volatility = xem[,3] - xem[,4]
xmr$volatility = xmr[,3] - xmr[,4]
xrp$volatility = xrp[,3] - xrp[,4]
zec$volatility = zec[,3] - zec[,4]
maid$volatility = maid[,3] - maid[,4]


n = 196

btc = btc[(nrow(btc)-n):nrow(btc),]
dash = dash[(nrow(dash)-n):nrow(dash),]
eth = eth[(nrow(eth)-n):nrow(eth),]
iota = iota[(nrow(iota)-n):nrow(iota),]
lsk = lsk[(nrow(lsk)-n):nrow(lsk),]
xem = xem[(nrow(xem)-n):nrow(xem),]
xmr = xmr[(nrow(xmr)-n):nrow(xmr),]
xrp = xrp[(nrow(xrp)-n):nrow(xrp),]
zec = zec[(nrow(zec)-n):nrow(zec),]
maid = maid[(nrow(maid)-n):nrow(maid),]

btc$ret = c(NA, diff(log(btc$close)))
dash$ret = c(NA, diff(log(dash$close)))
eth$ret = c(NA, diff(log(eth$close)))
iota$ret = c(NA, diff(log(iota$close)))
lsk$ret = c(NA, diff(log(lsk$close)))
neo$ret = c(NA, diff(log(neo$close)))
xem$ret = c(NA, diff(log(xem$close)))
xmr$ret = c(NA, diff(log(xmr$close)))
xrp$ret = c(NA, diff(log(xrp$close)))
zec$ret = c(NA, diff(log(zec$close)))
maid$ret = c(NA, diff(log(maid$close)))

btc = btc[2:nrow(btc), ]
eth = eth[2:nrow(eth), ]
dash = dash[2:197, ]
iota = iota[2:197, ]
lsk = lsk[2:197, ]
neo = neo[2:197, ]
xem = xem[2:197, ]
xmr = xmr[2:197, ]
xrp = xrp[2:197, ]
zec = zec[2:197, ]
maid = maid[2:197, ]
```

```{r}
#the next step is to create tables for each category of cryptocurrencies, and put some variables 

#for that we need to read the variables again, one by one, as done in the previous code.


total_perc_ret_btc = (btc$close[nrow(btc)] - btc$close[1])/btc$close[1]
print(total_perc_ret_btc)
total_perc_ret_eth = (eth$close[nrow(eth)] - eth$close[1])/eth$close[1]
print(total_perc_ret_eth)

mean_daily_vol_btc = mean(btc$volatility)
print(mean_daily_vol_btc)
mean_daily_vol_eth = mean(eth$volatility)
print(mean_daily_vol_eth) #much lower volatility

mean_price_btc = mean(btc$close)
mean_vol_to_mean_price_btc = mean_daily_vol_btc/mean_price_btc

mean_price_eth = mean(eth$close)
mean_vol_to_mean_price_eth = mean_daily_vol_eth/mean_price_eth

mean_daily_ret_btc = mean(btc$ret)
mean_daily_ret_eth = mean(eth$ret)

mean_daily_perc_vol_btc = mean(btc$volatility) / mean(btc$close)
mean_daily_perc_vol_eth = mean(eth$volatility) / mean(eth$close)


#we now need to take into account the google interest towards the cryptocurrencies

library(readr)
interest = read_csv('eth_btc_google.csv')
interest = data.frame(interest)
interest$btc = interest$btc/100
interest$eth = interest$eth/100
interest$date = as.Date(interest$date)

library(ggplot2)

btc_eth_int <- ggplot(data = interest, aes(x = date)) +
  geom_line(aes(y = btc, linetype = "btc")) +
  geom_line(aes(y = eth, linetype = "eth")) +
  ggtitle('                     Interest on btc and eth      ') +
  scale_linetype_discrete(name ="")
btc_eth_int


```
```{r}
returns = cbind(btc$ret, eth$ret, dash$ret, iota$ret, lsk$ret, neo$ret, xem$ret, xmr$ret, xrp$ret, zec$ret, maid$ret)
returns = data.frame(returns)
colnames(returns) = c("btc", "eth", "dash", "iota", "lsk", "neo", "xem", "xmr", "xrp", "zec", "maid")
```

```{r}
avg_interest_btc = mean(interest$btc)
avg_interest_eth = mean(interest$eth)
btc2 = read_csv('btc.csv')
nrow(btc2) #this number of observations is going to be used for taking the inverse of the time, so that we give more weight to currencies that have had good performance but are not still in the maturity stage, not even close (btc is also not in the maturity stage, but we expect ethereum to have more relevance in the coming years, as in less time it has done as much as bitcoin for the blockchain community, if not more)
inv_time_btc = 1 / (nrow(btc2) / 365) #0.1316264

eth2 = read_csv('eth.csv')
nrow(eth2)
inv_time_eth = 1 / (nrow(eth2) / 365) #0.3941685

#let's visualize the movement of the returns of both series
ggplot(data = returns, aes(x = seq(1, nrow(returns), 1))) +
  geom_line(aes(y = btc, linetype = "btc")) +
  geom_line(aes(y = eth, linetype = "eth")) +
  ggtitle('                                btc and eth returns') +
  scale_linetype_discrete(name = "")



```
```{r}
#this chunk contains all the rest of calculations for including in the excel spreadsheet (where the final computation of portfolio weights is carried out)

#anonymity cryptos
total_perc_ret_xmr = (xmr$close[nrow(xmr)] - xmr$close[1])/xmr$close[1]
total_perc_ret_zec = (zec$close[nrow(zec)] - zec$close[1])/zec$close[1]
total_perc_ret_dash = (dash$close[nrow(dash)] - dash$close[1])/dash$close[1]

mean_ret_xmr = mean(returns$xmr)
mean_ret_zec = mean(returns$zec)
mean_ret_dash = mean(returns$dash)


anonim_interest = read_csv('anonimity_cryptos_interest.csv')
anonim_interest = data.frame(anonim_interest)
anonim_interest$dash = anonim_interest$dash/100
anonim_interest$zec = anonim_interest$zec/100
anonim_interest$xmr = anonim_interest$xmr/100

mean_int_dash = mean(anonim_interest$dash)
mean_int_zec = mean(anonim_interest$zec)
mean_int_xmr = mean(anonim_interest$xmr)

mean_vol_dash = mean(dash$volatility)
mean_vol_zec = mean(zec$volatility)
mean_vol_xmr = mean(xmr$volatility)

mean_perc_vol_dash = mean_vol_dash / mean(dash$close)
mean_perc_vol_zec = mean_vol_zec / mean(zec$close)
mean_perc_vol_xmr = mean_vol_xmr / mean(xmr$close)

xmr2 = read_csv('xmr.csv')
nrow(xmr2)
inv_time_xmr = 1 / (nrow(xmr2) / 365)

zec2 = read_csv('zec.csv')
inv_time_zec = 1 / (nrow(zec2) / 365)

dash2 = read_csv('dash.csv')
inv_time_dash = 1 / (nrow(dash2) / 365)


xem2 = read_csv('xem.csv')
tot_perc_ret_xem = (xem$close[nrow(xem)] - xem$close[1]) / xem$close[1]
tot_perc_ret_xem

xrp2 = read_csv('xrp.csv')
tot_perc_ret_xrp = (xrp$close[nrow(xrp)] - xrp$close[1] ) / xrp$close[1]
tot_perc_ret_xrp

tot_perc_ret_neo = (neo$close[nrow(neo)] - neo$close[1]) / neo$close[1]
tot_perc_ret_neo

mean_daily_ret_xem = mean(xem$ret)
mean_daily_ret_xem
mean_daily_ret_xrp = mean(xrp$ret)
mean_daily_ret_xrp
mean_daily_ret_neo = mean(neo$ret)
mean_daily_ret_neo

platform_int = read_csv('platform_interest.csv')
platform_int = data.frame(platform_int)
platform_int$xrp[1:3] = c(0,0,0) #we clean the data to have only numbers. 
platform_int$xem = platform_int$xem/100
platform_int$xrp = as.numeric(platform_int$xrp)
#platform_int = gsub(pattern = '<1', x = platform_int, replacement = 0.5)
platform_int$xrp = platform_int$xrp/100
platform_int$neo = platform_int$neo/100

mean_vol_xem = mean(xem$volatility)
mean_vol_xrp = mean(xrp$volatility)
mean_vol_neo = mean(neo$volatility)
mean_vol_xem
mean_vol_xrp
mean_vol_neo

mean_perc_vol_xem = mean_vol_xem/mean(xem$close)
mean_perc_vol_xrp = mean_vol_xrp/mean(xrp$close)
mean_perc_vol_neo = mean_vol_neo/mean(neo$close)

inv_time_xem = 1/(nrow(xem2)/365)
inv_time_xrp = 1/(nrow(xrp2)/365)

neo2 = read_csv('neo.csv')
inv_time_neo = 1/(nrow(neo2)/365)


#now let's do the protocol currencies analysis
tot_perc_ret_iota = (iota$close[nrow(iota)] - iota$close[1]) / iota$close[1]
tot_perc_ret_lsk = (lsk$close[nrow(lsk)] - lsk$close[1]) / lsk$close[1]
tot_perc_ret_maid = (maid$close[nrow(maid)] - maid$close[1]) / maid$close[1]

mean_daily_ret_iota = mean(iota$ret)
mean_daily_ret_iota
mean_daily_ret_lsk = mean(lsk$ret)
mean_daily_ret_lsk
mean_daily_ret_maid = mean(maid$ret)
mean_daily_ret_maid


#now let us check the google interest in each of the protocol currencies

protocol_int = read_csv('protocol_interest.csv')

protocol_int$lsk = ifelse(protocol_int$lsk == "<1", 0.5, protocol_int$lsk) #we transform all values <1 to 0.5, as the expected mean between 0 and 1 is supposed to be this if the range behaves normally (bell-shaped).
protocol_int$maid = ifelse(protocol_int$maid == "<1", 0.5, protocol_int$maid)

protocol_int$iota = as.numeric(protocol_int$iota)
protocol_int$lsk = as.numeric(protocol_int$lsk)
protocol_int$maid = as.numeric(protocol_int$maid)

protocol_int$iota = protocol_int$iota/100
protocol_int$lsk = protocol_int$lsk/100
protocol_int$maid = protocol_int$maid / 100

avg_int_iota = mean(protocol_int$iota)
avg_int_lsk = mean(protocol_int$lsk)
avg_int_maid = mean(protocol_int$maid)

mean_vol_iota = mean(iota$volatility)
mean_vol_lsk = mean(lsk$volatility)
mean_vol_maid = mean(maid$volatility)

mean_vol_iota
mean_vol_lsk
mean_vol_maid


perc_vol_iota = mean_vol_iota / mean(iota$close)
perc_vol_lsk = mean_vol_lsk / mean(lsk$close)
perc_vol_maid = mean_vol_maid / mean(maid$close)

perc_vol_iota
perc_vol_lsk
perc_vol_maid

iota2 = read_csv('iot.csv')
inv_time_iota = 1 / (nrow(iota2) / 365)

lsk2 = read_csv('lsk.csv')
inv_time_lsk = 1 / (nrow(lsk2) / 365)

maid2 = read_csv('maid.csv')
inv_time_maid = 1 / (nrow(maid) / 365)

inv_time_iota
inv_time_lsk
inv_time_maid

```

